The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-02-24 src/ms.tex
start FITS <-> Time
Signed-off-by: nstarman <nstarkman@protonmail.com>

    The FITS Time standard paper defines the formats and keywords used to
    represent timing information in FITS files. The Astropy FITS package now
    provides support for reading and writing native Time table columns using
    this format. This is described within the FITS unified I/O interface and
    examples of usage can be found in the Astropy native objects (mixin columns)
    section.

    Implementation of this feature was made possible through the support of the
    Google Summer of Code 2017 program. To learn more about this project please
    see the final report, A mixin protocol for seamless interoperability.

>>>>

    As anyone who has worked with FITS files knows, the FITS standard is both
    detailed and very flexible. While this means FITS is useful across many
    domains, working with the files can be involved. Expanding on the WCS and
    related work, the \astropyfits package now provides support for reading and
    writing native \astropyTime table columns using the FITS Time standard
    \citep{FITS-Time:2015}. For backward compatibility, this feature may be
    turned off. Implementation of this feature was made possible through the
    support of the Google Summer of Code 2017 program.
    % TODO: is there a way to cite this
    To learn more about this project please see the final report,
    \href{https://aaryapatil.wordpress.com/2017/08/28/a-mixin-protocol-for-seamless-interoperability/}{A
    mixin protocol for seamless interoperability}.
